Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-28 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
add change in letter R1

Based on the analysis, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ appears to be the most sensitive test for classification purposes because it shows the largest distinction in mean values between the different land cover types, indicating it is better at differentiating between homogeneous and heterogeneous areas. However, CV and $\text{CV}_{\text{MnAD}}$ are also reliable with lower variability, making them good candidates depending on the specific application.

>>>>

Based on the analysis, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ appears to be the most sensitive test for classification purposes because it shows the largest distinction in mean values between the different land cover types, indicating it is better at differentiating between homogeneous and heterogeneous areas.
However, CV and $\text{CV}_{\text{MnAD}}$ test are also reliable with a lower variability, making them good candidates depending on the specific application.
